\normalfont\spacedallcaps{Language reclamation: Literature review}

### 2023-06-19 assignment-4/article.tex
Whitespace fixes
Solve 18.1

>>>>

\subsubsection*{Problem 18.1 solution}

We proceed by calculating $Var[x_t]$ using the standard laws of variance. In addition, we use the fact that $x_{t-1}$ and $\epsilon_t$ are independent, and that $Var[\epsilon_t] = \textbf{I}$ since $\epsilon_t$ is drawn from a standard multivariate normal distribution.

\begin{align*}
  Var[x_t] &= Var[\sqrt{1-\beta_t}\cdot x_{t-1} + \sqrt{\beta_t} \cdot \epsilon_t] \\
  &= Var[\sqrt{1-\beta_t}\cdot x_{t-1}] + Var[\sqrt{\beta_t} \cdot \epsilon_t] \\
  &= (1-\beta_t) Var[x_{t-1}] + \beta_t Var[ \cdot \epsilon_t] \\
  &= (1-\beta_t) \textbf{I} + \beta_t \textbf{I} \\
  &= \textbf{I}
\end{align*}
